MSDS6372 - Final Project

### 2018-03-31 MSDS6372_Final_Project_BBHOF.Rmd
Added predict calculation to logistic regression

# copy data set, remove Name from the raw data set, so it's not included in the model, also removing features to play with the model
BBHOF_logistic <- BBHOFRaw
dropcolumns <- c("Name", "StolenBaseRuns", "RunsScored", "OfficialAtBats", "RunsBattedIn", "OnBasePct", "Triples", "StrikeOuts", "AdjustedProduction")
BBHOF_logistic <- BBHOF_logistic[,!(colnames(BBHOF_logistic) %in% dropcolumns)]

# split the raw data into testing and training data
set.seed(101) # set seed so that same sample can be reproduced in future

# now selecting 75% of data as sample from total 'n' rows of the data  
sample <- sample.int(n=nrow(BBHOF_logistic), size=floor(.75*nrow(BBHOF_logistic)), replace=FALSE)

@@

>>>>

# copy data set, remove Name from the raw data set, so it's not included in the model, also removing features to play with the model
BBHOF_logistic <- BBHOFRaw
dropcolumns <- c("Name", "StolenBaseRuns", "StrikeOuts", "CaughtStealing", "StolenBases")
BBHOF_logistic <- BBHOF_logistic[,!(colnames(BBHOF_logistic) %in% dropcolumns)]

# split the raw data into testing and training data
set.seed(100) # set seed so that same sample can be reproduced in future

# now selecting 90% of data as sample from total 'n' rows of the data  
sample <- sample.int(n=nrow(BBHOF_logistic), size=floor(.90*nrow(BBHOF_logistic)), replace=FALSE)

@@

# predict based on the test data, type='response' output probabilities in the form of P(y=1|X)
fittedresults <- predict(model, newdata=test, type='response')

# there are some NAs in the fitted results...we need to check into that - not sure how that's possible if I'm removing the features with NAs
sum(is.na(fittedresults))

# if P(y=1|X) > 0.5 then y = 1 otherwise y=0
fittedresults <- ifelse(fittedresults > 0.5, 1, 0)

# calculate the mean of the fitted results that don't equal the observed result - IGNORE NAs
misClasificError <- mean(fittedresults != test$HOFMembership, na.rm=TRUE)

# print the output as 100% - error
print(paste('Accuracy',1-misClasificError))
